manuscript_figures

### 2024-05-29 scripts/manuscript_figures.Rmd
finished data and figure 2

@@

@@

>>>>

# remove control column, not needed
kelp.filt <- kelp.filt[ -c(5) ]

@@

# remove control column, not needed
fish.filt <- fish.filt[ -c(5) ]

@@

# Make Figure 2
```{r}

# Aggregate the data by year, site, and transect and compute mean values
aggregated_data <- merged.dat %>%
  group_by(YEAR, SITE, TRANSECT) %>%
  summarize(mean_fish_biomass = mean(Fish.Biomass..g.m2., na.rm = TRUE),
            mean_kelp_cover = mean(COVER, na.rm = TRUE)) %>%
  ungroup()

# Perform linear regression
lm_model <- lm(mean_fish_biomass ~ mean_kelp_cover, data = aggregated_data)
lm_summary <- tidy(lm_model)
lm_summary_stats <- summary(lm_model)  # Get model summary

# Extract R-squared and p-value
r_squared <- round(lm_summary_stats$r.squared, 2)
p_value <- signif(lm_summary$p.value[2], 2)

# Create scatter plot
figure.2 <- ggplot(aggregated_data, aes(x = mean_kelp_cover, y = mean_fish_biomass)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE, formula = y ~ x, color = "blue") +
  annotate("text", x = Inf, y = Inf, label = paste0("R^2 = ", r_squared, ", p = ", p_value), 
           hjust = 2, vjust = 4, size = 4, parse = FALSE) +
  labs(x = "Kelp cover (%)", y = "Fish biomass (g/m2)",
       title = "Fish Biomass vs Kelp Cover") +
  theme_classic(); figure.2
